ResultsNPS

### 2019-11-29 R/nps_reports/results.Rmd
reports. changes in datasets and filtering when not using logarithmic scale.

right_tail <- default_tail
quality_degr_all_filt <- 
  quality_degr_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0, really_small_number, dif_perc)) %>%
  filter(dif_perc %>% value_filt_tails(c(0, right_tail)))

@@

quality_perf_all_filt <- 
  quality_perf_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0, really_small_number, dif_perc)) %>%
  filter(dif_perc %>% value_filt_tails(c(each_tail, each_tail)))
```

@@

```{r soft_constraints}
right_tail <- default_tail
errors_stats <- get_soft_constraints(df)
errors_all <- get_soft_constraints_2(df) %>% 
  mutate(dif= if_else(dif<=0, really_small_number, dif))

>>>>

right_tail <- default_tail
quality_degr_all_filt <- 
  quality_degr_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0 & scale!='identity', really_small_number, dif_perc)) %>%
  filter(dif_perc %>% value_filt_tails(c(0, right_tail)))

@@

quality_perf_all_filt <- 
  quality_perf_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0 & scale!='identity', really_small_number, dif_perc)) %>%
  filter(dif_perc %>% value_filt_tails(c(each_tail, each_tail)))
```

@@

```{r soft_constraints}
right_tail <- default_tail
errors_stats <- get_soft_constraints(df)
errors_all <- get_soft_constraints_2(df) %>% 
  mutate(dif= if_else(dif<=0 & scale!='identity', really_small_number, dif))
